Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-07-15 latex/paper.tex
organized plots

\GB{ask Haesun to write intro paragraph motivating hierarchical clustering but noting the limitations of time and data size}

@@

	The HYDICE image is flattened from $1280\times 307\times 191$ to $191\times 392960$ and the AVIRIS image is likewise
	flattened from $8940\times 747\times 224$ to $224\times 6678180$. Unlike with document clustering, hyperspectral image sizes grow in pixels
	and not spectral bands. So, for both images, large scaling is impossible given our current data distribution.
	\LM{I think this is awkward and I'm not sure if we need to include it}

@@

\GB{Lawton, can you gather this data, Ramki can you visualize it?}
\begin{itemize}
	\item compare 1D distribution scaling with optimal 2D grid scaling
	\item use synthetic short-and-fat dense and squarish sparse
\end{itemize}

@@

\GB{Ramki, can you add a bar plot to show time breakdown across complete levels?  Let's do Aviris and PubMed; just use levels data file}

\subsubsection{Weak Scaling}

\GB{maybe this section is lower priority}
\begin{itemize}
	\item dense and sparse
\end{itemize}

\subsubsection{Strong Scaling}

\include{plots}

\begin{itemize}
	\item big dense synthetic
	\item big sparse synthetic
	\item Aviris
	\item PubMed
\end{itemize}

\subsection{Clustering}

@@

\GB{Lawton, show some visualization of the tree}

\subsubsection{Document Corpus}

\GB{Lawton, show a visualization of top words in tree}

>>>>

\GB{Prof Park, can you draft an introduction?  We are focusing on the dense case and using HSI and image clustering as applications.  Section 4 is still unfinished, but nearly all of the performance plots are there.  Feel free to leave placeholders for details that aren't obvious, we can clean them up Wednesday night.}

@@

	The HYDICE image is flattened from $1280\times 307\times 191$ to $191\times 392960$ and the AVIRIS image is likewise
	flattened from $8940\times 747\times 224$ to $224\times 6678180$. Unlike with document clustering, hyperspectral image sizes grow in pixels
	and not spectral bands. So, for both images, large scaling is impossible given our current data distribtion.
	\LM{I think this is awkward and I'm not sure if we need to include it}

@@

\GB{4 plots: 2 data sets with speedup/breakdown}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_rank2_strongscaling.pdf}
\caption{Relative Time Breakdown for Rank-2 NMF \cref{alg:parrank2nmf} Strong Scaling at Level-0}
\label{fig:synrank2strongscaling}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_rank2_speedup.pdf}
\caption{Strong Scaling Speedup for Rank-2 NMF \cref{alg:parrank2nmf} at Level-0}
\label{fig:synrank2speedup}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/realworld_rank2_strongscaling.pdf}
\caption{Relative Time Breakdown for Rank-2 NMF \cref{alg:parrank2nmf} Strong Scaling at Level-0 on Realworld Data}
\label{fig:rwrank2strongscaling}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/realworld_rank2_speedup.pdf}
\caption{Strong Scaling Speedup for Rank-2 NMF \cref{alg:parrank2nmf} at Level-0 on Realworld Data}
\label{fig:rwrank2speedup}
\end{center}
\end{figure}

\subsubsection{Hierarchical Clustering Strong Scaling}

\GB{4 plots: 2 data sets with speedup/breakdown}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_hierarchical_speedup.pdf}
\caption{Strong Scaling Speedup for Hierarchical Clustering. The total time taken for complete Hierarchical Clustering \cref{alg:hiernmf2}}
\label{fig:synhierspeedup}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_hier_strongscaling.pdf}
\caption{Relative Time Breakdown for Hierarchical Clustering. The plot uses the total time taken for complete Hierarchical Clustering \cref{alg:hiernmf2}}
\label{fig:synhierstrongscaling}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/realworld_hierarchical_speedup.pdf}
\caption{Strong Scaling Speedup for Hierarchical Clustering on Realworld Data. The total time taken for complete Hierarchical Clustering \cref{alg:hiernmf2}}
\label{fig:rwhierspeedup}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/realworld_hier_strongscaling.pdf}
\caption{Relative Time Breakdown for Hierarchical Clustering on Realworld. The plot uses the total time taken for complete Hierarchical Clustering \cref{alg:hiernmf2}}
\label{fig:rwhierstrongscaling}
\end{center}
\end{figure}

@@

\GB{3 plots: for synthetic level breakdown for 1 node and for 40 nodes; for realworld just for 80 nodes

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_sequential_level_breakdown.pdf}
\caption{Sequential Breakdown plot for levels 0 to 5. y-axis is absolute wall clock time in seconds}
\label{fig:seqlevelbreakdown}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_parallel_level_breakdown.pdf}
\caption{Parallel Breakdown plot for levels 0 to 5 on 40 nodes. y-axis is absolute wall clock time in seconds}
\label{fig:parallellevelbreakdown}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/realworld_parallel_level_breakdown.pdf}
\caption{Parallel Breakdown plot for levels 0 to 5 on 80 nodes. y-axis is absolute wall clock time in seconds}
\label{fig:rwparallellevelbreakdown}
\end{center}
\end{figure}

\subsection{DC Clustering Results}

@@
